---
title: "Using FarsPackage and fars function"
author: "Karol Michelle Sandoval"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using FarsPackage and fars function}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(FarsPackageKarol)
```

## 1. fars_read

This is a function that allows you to load all types of 
documents with .csv extension. You can load these documents
using the filename argument followed by the .csv extension 
inside double quotes and you will get a data frame in tibble 
format to work in the console. For example:

```{r setup1,eval = F}
fars_read("accident_2013.csv.bz2")
fars_read("accident_2014.csv.bz2")
```

## 2. make_filename

This function allows you to generate character objects 
containing a formatted combination of input values. For example:

```{r setup2,eval = F}
make_filename(2013)
make_filename(2014)
```

## 3. fars_read_years 

Function that takes a set of years to generate file names and thus extract the month and year corresponding to each record in the dataset.

```{r setup3,eval = F}
fars_read_years(c(2013,2014))
```

## 4. fars_summarize_years

Function that takes a set of years and calls the function fars_read_years, then joins them together and at the end you get a summary of the data.

```{r setup4,eval = F}
fars_summarize_years(c(2013,2014))
```


## 5. fars_map_state

This function takes the state number and plots the accidents per selected year.


```{r setup5,eval = F}
fars_map_state(1,2013)
```
